---
title: "data_explore.rmd"
output: 
  html_document:
    keep_md: yes
---
Names: Natalie, Zoe, and Aiym
```{r setup, include=FALSE}
library(fivethirtyeight) 
library(ggplot2)
library(ggridges)
library(tidyverse)
library(broom)
library(moderndive)
```

Describing Data and Research Question:

Our data is an analysis of Bob Ross's paintings that show when certain elements of nature such as trees or waves appear in his work. This dataset comes from the fivethirtyeight package in R studio and it was collected by counting the number of certain objects in 403 of his paintings. We hope to learn more about how specific elements in his paintings influence the likelihood that a tree will appear in that same artwork.

Question: We will work to examine how the frequencies of specific variables in his paintings affect the likelihood of other elements appearing in his works. 

```{r}
bob_ross <- bob_ross
```

```{r}
ggplot(data = bob_ross) +
    geom_histogram(aes(x = tree), fill = "lightblue", color= "white", bins = 10)
```
The vast majority of Bob Ross's painting have trees in them 


```{r}
ggplot(data = bob_ross) +
    geom_histogram(aes(x = snow), fill = "lightblue", color= "white", bins = 10)
```


```{r}
ggplot(bob_ross)+
  geom_jitter(aes(x=season, y= factor(tree), color= factor(lake)))+
  facet_wrap(~tree)
```
If there is a lake in one of his paintings it is very likely that there will also be a tree because There is only one of his paintings that has a lake and no trees. 
```{r}
ggplot(data=bob_ross) +
  geom_bar(mapping = aes(x=tree, fill=factor(lake))) 
```


```{r}
glm_tree <- glm(tree ~ lake,
                  data= bob_ross, family=binomial)
tidy(glm_tree)
```
```{r}
tidy(glm_tree) %>% 
  select(term, estimate) %>% 
  mutate(exp_est = exp(estimate))
```

On average, the presence of a lake in a painting increases the odds of having a tree in the painting by 26.584474. This makes sense and is in accordance with what we expected from the graph above. There is only one lake in all of his paintings, which doesn't have a tree paired with it. We chose to fit this model because our graph of tree and lake had an interesting relationship that we wanted to investigate further.


```{r}
glm_cloud <- glm(tree ~ lake+clouds,
                  data= bob_ross, family=binomial)
tidy(glm_cloud)
```
```{r}
tidy(glm_cloud) %>% 
  select(term, estimate) %>% 
  mutate(exp_est = exp(estimate))
```
We chose to produce this model because we wanted to see if adding an extra independent variable is going to change the relationship between lake and tree. By adding the additional independent variable, the odds for the lake coefficient increase to 28.21, on average. The presence of clouds in a painting increases the odds of a tree being present in the painting by 0.20, on average.  

```{r}
set.seed(111)
boot_ross <-
  bob_ross %>% 
  rep_sample_n(size = 403, replace = TRUE, reps = 200) %>% 
  group_by(replicate) %>% 
  do(glm(tree ~ lake, data=.) %>% tidy()) %>%
  filter(term == "lake")

boot_ross %>% 
  ggplot() +
  geom_histogram(aes(x=estimate))

boot_ross %>%
  summarize(mean_est = mean(estimate),
            se_est = sd(estimate))
```

This is a histogram showing the bootstrap distribution of the average likelihood that a lake is in the painting. The mean is 16.9% and SD is 19.8%.



```{r}
estimated_coeff <- tidy(glm_tree)%>%
  pull(estimate)

bootstrap_bob_ross%>%
  summarise(
    se= sd(estimate),
    lower_q = 1.675500	 - 2*se,
    upper_q = 1.675500	 + 2*se)
      
```


Next research steps: 

Would could find and evalute statistics for our models and graphs such as mean and standard deviation. We used bootstrapping in this assignment but we could also conduct a hypothesis and test it to predict if there is a relationship between certain object in Bob Ross's paintings.
