---
title: "data_explore.rmd"
output: 
  html_document:
    keep_md: yes
---
Names: Natalie, Zoe, and Aiym
```{r setup, include=FALSE}
library(fivethirtyeight) 
library(ggplot2)
library(ggridges)
library(tidyverse)
library(broom)
library(moderndive)
```


```{r}
drug_use <- drug_use
```


```{r}
ggplot(data = drug_use) +
    geom_point(aes(x = age, y = alcohol_use))
```
There is an increase in alcohol use beginning in the late teens which continues until the age of 21-23. After age 23, alcohol use then beings to decrease as age increases.

```{r}
ggplot(data = drug_use) +
    geom_point(aes(x = age, y = heroin_use))
```
Heroin use is low among young teens and adults over 35. It is highest for people in their early 20's.

```{r}
ggplot(data = drug_use) +
    geom_histogram(aes(x = heroin_freq), fill = "lightblue", color= "white", bins = 30)+
  xlab("Heroin Frequency")
```
Most heroin users have used the drug between 25-75 times and only a small number have used heroin more than 100 times. 

```{r}
lm_alcohol <- lm(alcohol_use ~ age,
                 data=drug_use)
get_regression_table(lm_alcohol)
```

```{r}
lm_drug <- lm(alcohol_use ~ marijuana_use,
                 data=drug_use)
get_regression_table(lm_drug)
```

```{r}
ggplot(data = bob_ross) +
    geom_histogram(aes(x = tree), fill = "lightblue", color= "white", bins = 30)
```
The vast majority of Bob Ross's painting have trees in them 

```{r}
ggplot(data = bob_ross) +
    geom_histogram(aes(x = beach), fill = "lightblue", color= "white", bins = 30)
```
Only a small number of Bob Ross's painting contain a beach 

```{r}
lm_tree <- lm(tree ~ apple_frame,
                 data= bob_ross)
get_regression_table(lm_tree)
```


```{r}
lm_tree <- lm(palm_trees ~ beach,
                 data= bob_ross)
get_regression_table(lm_tree)
```

