---
title: "data_explore.rmd"
output: 
  html_document:
    keep_md: yes
---
Names: Natalie, Zoe, and Aiym
```{r setup, include=FALSE}
library(fivethirtyeight) 
library(ggplot2)
library(ggridges)
library(tidyverse)
library(broom)
library(moderndive)
```

Describing Data and Research Question:

Our data is an analysis of Bob Ross's paintings that show when certain elements of nature such as trees or waves appear in his work. This dataset comes from the fivethirtyeight package in R studio and it was collected by counting the number of certain objects in 403 of his paintings. We hope to learn more about how specific elements in his paintings influence what other objects will appear in that same artwork.

Question: We will work to examine how the frequencies of specific variables affect the likelihood of other elements appearing in his works. 

```{r}
ggplot(data = bob_ross) +
    geom_histogram(aes(x = tree), fill = "lightblue", color= "white", bins = 30)
```
The vast majority of Bob Ross's painting have trees in them 

```{r}
ggplot(data = bob_ross) +
    geom_histogram(aes(x = beach), fill = "lightblue", color= "white", bins = 30)
```
Only a small number of Bob Ross's painting contain a beach 

```{r}
lm_tree <- lm(tree ~ apple_frame,
                 data= bob_ross)
get_regression_table(lm_tree)
```


```{r}
lm_tree <- lm(palm_trees ~ beach + waves,
                 data= bob_ross)
get_regression_table(lm_tree)
```

